

Let $\kappa, n \in \NN$. 
Recall the Praos beacon with parameters $\kappa$ and $n$ from Definition~\ref{def:praos-beacon}. 
The goal of this \Section is to state our main results 
about the quality of the Praos beacon 
in terms of its min-entropy after multiple epochs (Definition~\ref{def:beacon-security}).

As we have done in the modeling of the consistency problem 
(\Section~\ref{sec:model-multihonest}), 
we start by defining the so-called ``characteristic string'' $w$. 
It captures the outcomes of the private leader election process $\PrivateLeaderElection$ 
in these slots. 
Next, we use the definition of the Praos beacon protocol to 
derive an expression for its grinding power on $w$.
Next, for some $\epsilon \in (0,1)$, 
we define a distribution $\mathcal{L}((1-\epsilon)/2)$ on the set of characteristic strings of length $n$; 
this represents the outcome of $\PrivateLeaderElection((1-\epsilon)/2)$, i.e., 
a private leader election with an adversarial stake-minority.
We finish this \Section by stating our main theorem about the min-entropy loss in the Praos beacon. 
The proof of this theorem is presented in \Section~\ref{sec:praos-second-moment}.




% \newcommand{\Suffix}[2]{ {#1}^{\overset{#2}{\leftarrow} } }
% \newcommand{\Suffix}[2]{ {#1}[-{#2}:] }
\newcommand{\Suffix}[2]{ \mathsf{suffix}({#1},{#2})}
\newcommand{\CoinTossingLC}{\Pi_\mathsf{lc}^{\Players(\alpha),k,n}}



% Let $\EpsP \in (0,1)$ and $s, k \in \NN$. 
% Let $\Blockchain$ be an $(\EpsP, k, s)$-secure eventual consensus PoS blockchain protocol 
% under the longest-chain rule, such as 
% Ouroboros Praos~\cite{Praos} and Snow White~\cite{SnowWhite}. 
% Let $\kappa, n$ be two positive integers. 
% Recall the beacon protocol from Section~\ref{sec:praos-model-grindingpower-minentropy}.
% Let $L \in \NN$ and suppose that 
% the blockchain protocol $\Blockchain$ is $(\EpsP, k, s)$-secure 
% inside an epoch. 
% Let $R_L$ be the number of ``resets'' 
% that the adversary can cause to the beacon, 
% i.e., 
% the number of candidate values for $\eta_L$ 
% is chosen (by the protocol) 
% from a set of size $R_L$. 
% Then the min-entropy loss 
% in the beacon output $\eta_L$ 
% is $\log_2(R_L)$. 
% We want to show that with high probability, 
% this quantity is bounded from above by 
% a suitable function. 
% The probability in the preceding statement 
% depends on 
% the randomness in $\eta_0$ and 
% the outcomes of the leader election inside the $\Blockchain$, 
% i.e., whether a block (and hence its nonce) is emitted by an honest player.



\ignore{

\iftoggle{drawfigs}{

  \begin{figure}
    \centering
    \pgfmathsetmacro{\k}{100}
    \pgfmathsetmacro{\d}{1}
    \pgfmathsetmacro{\T}{24 * \k}
    \pgfmathsetmacro{\tau}{30}
    \pgfmathsetmacro{\n}{(\T - \k)/\d}
    \pgfmathsetmacro{\ell}{\k/\d}
    \pgfmathsetmacro{\ellPlusN}{\ell + \n}
    \begin{tikzpicture}[trim axis left,
      declare function={
        rho_praos_small_alpha(\a) = log2(\n + \ell) + \tau / 2 ; 
        rho_praos_mid_alpha(\a) = log2(\n + \ell) + \tau / 2 + \n * (0.067 + 1.92*\a - 1.44 * \a * \a) ; 
        rho_praos_large_alpha(\a) = log2(\n + \ell) + \tau / 2 + \n * (0.237 + 0.86 * \a); 
        % rho_geom_small_alpha(\a) = 2 * log2(\n) + \tau/2 + \ell * log2( sqrt(1 + \a)/(1 - \a) );
        % rho_geom_large_alpha(\a) = 2 * log2(\n) + (\tau + \ell * log2( 1/\a ) )/(2 - (3 * \a - 1)/(2 * \a * \a));
      }
      %    declare function = { entropy(\x) = 1; },
      ]
      \begin{axis}[domain=0:0.5,
        samples=100,
        enlarge x limits=false,
        grid=both,
        no markers,
        x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
        y label style={at={(axis description cs:-0.1,.5)},anchor=south},
        xlabel={$\alpha$, relative adversarial stake},
        ylabel={$\rho$, loss in min-entropy (bits)},
        % there is one default value for the `legend pos' that is outside the axis
        legend pos=south east,
        % (so the legend looks a bit better)
        legend cell align=left
        ]
        \addplot +[thick,domain=0:(0.0955),red,forget plot] plot (\x, {rho_praos_small_alpha(\x)});
        \addplot +[thick,domain=0.0955:(1/3),red,forget plot] plot (\x, {rho_praos_mid_alpha(\x)});
        \addplot +[thick,domain=(1/3):(0.5),red,legend] plot (\x, {rho_praos_large_alpha(\x)});
        \addlegendentry{Praos}

        % \addplot +[thick,domain=0:(1/3),blue,forget plot] plot (\x, {rho_geom_small_alpha(\x)});
        % \addplot +[thick,domain=(1/3):(1/2),blue,legend] plot (\x, {rho_geom_large_alpha(\x)});
        % \addlegendentry{$(\ell, \n, \alpha)$-geometric game, $d = 1$}
      \end{axis}
    \end{tikzpicture}
    \caption{Min-entropy loss in Praos. 
    Here, we assumed the consistency parameter $k = \k$ and 
    the probability of a consistency violation is $\EpsP = 2^{-\tau}$.
    Nonces from the first $T = 24\k$ slots contribute to the beacon.}
    % \caption{Min-entropy loss in Praos (red) and in the $(\ell, n, \alpha)$-geometric game (blue).}
    \label{fig:rho-praos}
  \end{figure}

} % end iftoggle{drawfigs}


}




\section{The characteristic string}
In Praos and Snow White, 
during each slot, 
each player determines privately and independently 
whether he is a leader for this slot. 
The probability that he succeeds is proportional to his stake. 
Naturally, this means there are empty slots 
which actually help the protocol achieve 
security even with network delay. 
However, since empty slots do not contribute in any blocks, 
we ignore them in our exposition. 
Hence we focus on a leader election process that assigns, 
to each slot, 
a non-empty subset of participants; 
these are the leaders at that slot. 
A leader is eligible to add a block to a 
maximum-length blockchain in his view. 
We can represent the outcome of this leader election scheme 
as a \emph{characteristic string}:


\begin{definition}[Characteristic string]\label{def:char-string-praos}
  A \emph{characteristic string} $w \in \{\A, 1, 2, 3, \ldots \}^*$ 
  corresponds to a particular execution of $\Blockchain$.
  For each slot $t = 1, 2, \ldots$, 
  $w_t = \A$ if $t$ is assigned to an adversarial participant; and 
  $w_t = k \in \{1,2,\ldots\}$ if $t$ is assigned to $k$ honest participants.
  By convention, $w_0 = 1$.
\end{definition}

Note that the above definition of characteristic strings 
is a generalization of Definition~\ref{def:trivalent-char-string}
in that it counts the number of honest leaders. 


For two characteristic strings $x$ and $w$ on the same alphabet, 
we write $x \Prefix w$ iff $x$ is a strict prefix of $w$. 
Similarly, 
we write $x \PrefixEq w$ iff either $x = w$ or $x \Prefix w$. 
The empty string $\varepsilon$ is a prefix to all strings. 
If $w_t = \A$, we say that ``$\Slot_t$ is adversarial;'' 
otherwise, we say that ``$\Slot_t$ is honest.'' 
Define $\#_\A(w)$ as the number of occurrences of $\A$ in $w$. 
Define $\#_\h(w) \triangleq |w| - \#_\A(w)$.
A slot $t$ is called \emph{$k$-honest} if $w_t = k \in \NN$.
A characteristic string $w$ is called $\Hheavy$ if 
$\#_\h(w) > \#_\A(w)$; 
otherwise, $w$ is called $\Aheavy$. 
We use $w[i : j]$ to denote the substring $w_i w_{i+1}\ldots w_j$.



% As we discussed after Definition~\ref{def:coin-flipping-security}, 
% the adversarial participants in an $(\EpsP, \rho)$-secure 
% coin-flipping protocol $\Pi$ can choose the output $\eta$ 
% from a set $X$ of size $2^\rho$. 
% As $\Pi$ is conducted on the blockchain protocol $\Blockchain$, 
% the elements of $X$ are determined by 
% the set $C$ of all possible maximally long blockchains 
% at (or after) slot $n + k$. 
% Due the the $\kSlotCP$ property of $\Blockchain$, 
% these chains contain the same blocks corresponding to slots $1, \ldots, n$. 
% It follows that $\rho = \log_2 |X| = \log_2 g$.
% We call $g$ the \emph{grinding power} of the adversary. 





\section{Understanding the grinding power (GP)}

We briefly recall some fork-theoretic concepts
developed in Section~\ref{sec:viable-blockchains-adv-extensions}. 
Consider an abstract execution of $\Blockchain$ 
corresponding to the characteristic string $w$ 
where 
all blockchains are arranged in a rooted tree; 
this tree is called a \emph{fork}. 
If a block $B$ is issued from slot $t$, 
we say that $B$ has label $t$.
Two blockchains $\Chain_1, \Chain_2$ in a fork $F$ are considered ``different'' 
if and only if there is a slot from which 
$\Chain_1$ contains a block but $\Chain_2$ does not. 
A blockchain $\Chain \in F$ is called \emph{viable} (or \emph{competitive}) 
if the length of $\Chain$, denoted by $|\Chain|$, 
is at least $\#_\h(w)$. 
The rationale is that an honest blockchain $\Chain$ is broadcast immediately 
and hence any blockchain adopted by a future honest leader
must be at least as long as $\Chain$. 
% In addition, if an honest participant is presented with 
% a blockchain $\Chain$ with length at least $\#_\h(w)$, 
% that participant would possibly prefer $\Chain$ 
% over a blockchain containing only honestly-emitted blocks 
If an honest observer (or leader) has to choose from multiple viable blockchains for adoption, 
we assume that the tie is broken by the adversary. 

Considering any fork $F$ and an honest blockchain $\Chain$ in $F$, 
a \emph{viable adversarial extension of $\Chain$} 
is an adversarial blockchain $\Chain' \in F$ 
such that $\Chain \Prefix \Chain'$, 
$\Chain'$ has the maximum length in $F$, 
and, importantly, $\Chain'$ contains only adversarial blocks after the prefix $\Chain$. 
Note that every adversarial extension 
viable at the onset of slot $n + 1$, 
corresponds to a choice 
for the output of the coin-flipping protocol. 
Each of these extensions contains a last honest block as its prefix. 
Thus we focus on upper bounding, 
over all forks for a given characteristic string, 
the total number of viable adversarial extensions 
of the honest blocks.
Note that a prerequisite to creating an adversarial extension 
of an honest block with label $h$ is that 
the suffix $w[h + 1 : n]$ must be $\Aheavy$.
We formalize this notion in the definition below.

\begin{definition}[Grinding Power]\label{def:option-sequence}
  Let $w$ be a characteristic string of length $n$. 
  We say that a sequence
  $
    0 \leq i_0 < i_1 < \cdots < i_k \leq n
  $
  is an \emph{option sequence} if
  \InlineCases{
    \item $i_0 = 0$ or 
    % $w_{i_0} = \h$, 
    $i_0 \neq \A$, 
    \item $w_{i_j} = \A$ for each $j > 0$, and
    \item $k \geq \#_\h(w[i_0 +1 : n])$.
  }
  We define the \emph{grinding power} of $w$, denoted $g(w)$, 
  as the 
  number of distinct option sequences for $w$.
\end{definition}


% \Paragraph{Grinding power of a characteristic string.}
Let $w = xy$ be a characteristic string. 
Define
\begin{equation}\label{eq:S_y}
    % S(d, z) 
    % \defeq \sum_{i \geq z}^{d - z}{ \binom{d - z}{i} } 
    S(y) 
    \defeq \sum_{i \geq \#_\h(y)}^{\#_\A(y)}{ \binom{\#_\A(y)}{i} } 
    % \,.
\end{equation}
and notice that it is the number of viable blockchains $\Chain$
in an execution on $w$ 
so that the last honest block in $\Chain$ occurs in slot $|x|$. 
By summing over all honest slots, 
the total number of viable blockchains for $w = w_1 w_2 \cdots w_n$,
i.e., the grinding power for $w$, is 
\begin{equation}\label{eq:g_praos}
    % g(w) 
    % = \sum_{\substack{
    %     x,y : w = xy, \\ 
    %     |x| \geq 0, \text{and}\\ 
    %     \text{slot $|x|$ is honest} }
    %   } w_{|x|}\, S(y)
    % \,.  
    g(w_1 w_2 \cdots w_n) 
    = \sum_{ \text{$t \in [n] : w_t$ is honest} }
      w_t\, S(w_{t+1} \cdots w_n)
    \,.  
\end{equation}





\section{The distribution \texorpdfstring{$\mathcal{L}(\alpha)$}{on characteristic strings}}
Let $\alpha \in (0, 1/2)$ 
and assume that the adversarial players control an $\alpha$ 
fraction of the stake. 
We consider a leader election mechanism 
which mimics the Praos election except the empty slots. 
Specifically, 
our (idealized) leader election mechanism 
induces 
a distribution $\mathcal{L}_n(\alpha)$ 
on length-$n$ characteristic strings $w = w_1 \ldots w_n$. 
We define $\mathcal{L}_n(\alpha)$ as follows: 
the symbols $w_i$s are independent 
and 
every slot is assigned to at least one slot leader. 
In addition, for all $i$, $\Pr[w_i = \A] = \alpha$.
Furthermore, $\Pr[w_i = j], j \in \NN$ is defined as follows: 
Let $m \in \NN$ be the total number of honest participants. 
Consider the independent Bernoulli random variables $X_i \in \{0, 1\}, i \in [m]$ 
and a tuple $(\sigma_1, \ldots, \sigma_m) \in [0,1]^m$ 
so that $\Pr[X_i = 1] = \sigma_i$ 
and $\sum \sigma_i = 1 - \alpha$. 
Let $H = H_m = \sum_{i =1}^m X_i$. 
Then for $i \in [n]$, 
$$
  \Pr[w_i = j] = (1-\alpha)\cdot
    \frac{\Pr[H = j \mid j \geq 1]}{1 - \Pr[H = 0]}
    \,.
$$

When $n$ is understood from the context, 
we just write $\mathcal{L}(\alpha)$ to denote this distribution. 
Furthermore, let $\epsilon \in (0,1)$ and set 
the adversarial stake $\alpha = (1-\epsilon)/2$. 
We define 
\begin{equation}\label{eq:praos-gneps}
  g(n,\epsilon) = g(W) \qquad \text{where} \quad W \sim \mathcal{L}_n((1-\epsilon)/2)
\end{equation}
as \emph{the grinding power over $n$ slots with adversarial stake $(1-\epsilon)/2$.}
Our goal is to derive tail bounds on $g(n,\epsilon)$.














\section{Main theorem: Praos beacon}
Define 
\begin{align}
  \phi(\epsilon) &\triangleq \frac{3}{2} \left( (1-\epsilon^2) (1-\epsilon) \right)^{1/3}\label{eq:phi_eps} \\
  V(\epsilon) &= \begin{cases}
      \left( (5-3 \epsilon)/2 \right)^s & \text{if}\quad 0 < \epsilon \leq 1/3\,, \\
      \left( 2^{2/3} \phi(\epsilon) \right)^s & \text{if}\quad 1/3 < \epsilon \leq 3/5\,, \\
      \left( (5/3) \phi(\epsilon) \right)^s & \text{otherwise}\,. 
    \end{cases} 
  \,. \label{eq:V-eps-praos}
\end{align}
\noindent


Let $\epsilon \in (0,1), \alpha = (1-\epsilon)/2, n \in \NN$. 
We can prove that 
conditioned on an $(\EpsP, k, s)$-secure execution of Praos in an epoch of length $n$ 
and characteristic string $W \sim \mathcal{L}_n(\alpha)$, 
$\Exp[g(n,\epsilon)^2] = O(s^2) V(\epsilon)$.
In Figure~\ref{fig:praos-gp-moments}, 
we have plotted various moment bounds on $g(n,\epsilon)$; 
we will prove these bounds next in this exposition.

\iftoggle{drawfigs}{
  \input{grinding-praos/fig-praos-gp-moment-bounds}
}

We can derive tail bounds on $g(n,\epsilon)$ using the second moment bound.

\begin{theorem}[Praos beacon]\label{thm:minentropy-loss-praos-multi-epochs}  
  Let $\epsilon \in (0, 1)$ and $L,\kappa \in \NN$. 
  Recall $\phi(\epsilon)$ from~\eqref{eq:phi_eps}.
  Suppose Praos 
  remains $(\EpsP, k, s)$-secure 
  inside any epoch 
  with a characteristic string $W \sim \mathcal{L}((1-\epsilon)/2)$. 
  Let 
  \begin{align}
    \rho &= \begin{cases}
      % Ignoring the additive factor \log_2(0.4 (1+2\epsilon) )/2
      s/2 \cdot \log_2\left( (5-3 \epsilon)/2 \right) + \log_2(s)  & \text{if}\quad 0 < \epsilon \leq 1/3\,, \\
      s/2 \cdot \log_2\left( 2^{2/3} \phi(\epsilon) \right) + \log_2(s) & \text{if}\quad 1/3 < \epsilon \leq 3/5\,, \\
      s/2 \cdot \log_2\left( (5/3) \phi(\epsilon) \right) + \log_2(s) + 0.14 & \text{otherwise}\,. 
    \end{cases}
    \label{eq:rho-praos-multiepoch}
  \end{align}

  Let $\eta \in \{0,1\}^\kappa$ be the output of the beacon after $L$ epochs.
  % and $L \in \NN$ so that $L \sqrt{m \EpsP} \leq 1$. 
  Then $g(n,\epsilon) \leq 2^\rho$ except with probability at most $3 L s \EpsP^{1/2} V(\epsilon)^{1/2}$.
  Equivalently,
  $$
    \Pr_{W \sim \mathcal{L}((1-\epsilon)/2)}[H_\infty(\eta) \geq \kappa - \rho] 
      \leq 1 - 3 L s \EpsP^{1/2} V(\epsilon)^{1/2} \,.
  $$
  In particular, for $\epsilon > 0.809$, 
  $\rho = \Poly(\log_2 s)$ and $g(n,\epsilon) = O(s)$ 
  except with probability at most $3Ls \EpsP^{1/2}$.
\end{theorem}
\noindent
The proof of Theorem~\ref{thm:minentropy-loss-praos-multi-epochs} 
is presented in Section~\ref{sec:proof-praos-theorem}. 

\begin{remark*}
  When $\epsilon < 0.809$, 
  the $O(s)$ term in the min-entropy loss $\rho$ 
  is inevitable sine, at this region, 
  $g(n,\epsilon) = e^{\Omega(s)}$.
  The factor $1/2$ in the leading term in $\rho$ 
  is the result of using the second-moment method 
  to derive the tail bound.
\end{remark*}
\iftoggle{drawfigs}{
  \input{grinding-praos/fig-praos-multi-epoch}
}




% Let $\Suffix{w}{d}$ denote the length-$d$ suffix of a string $w$.

