





\section{\texorpdfstring{The distribution $\DistL$}{A distribution} on characteristic strings}\label{sec:Lalpha-praos}

Let $\alpha \in (0, 1/2)$ 
and assume that the adversarial players control an $\alpha$ 
fraction of the stake. 
We consider a leader election mechanism 
which mimics the Praos election except the empty slots. 
Specifically, 
our (idealized) leader election mechanism 
induces 
a distribution $\mathcal{L}_n(\alpha)$ 
on length-$n$ characteristic strings $w = w_1 \ldots w_n$. 

\begin{definition}[$\mathcal{L}_n(\alpha)$]\label{def:dist-L-alpha-praos}
  Let $\alpha \in (0,1/2)$ and $n \in \NN$. 
  $\mathcal{L}_n(\alpha)$ is a distribution on characteristic strings 
  $w = w_1 \ldots w_n$ so that 
  the symbols $w_i$s are independent and identically distributed as follows: 
  $\Pr[w_i = \A] = \alpha$ and 
  % $\Pr[w_i = \perp] = 0$.
  $\Pr[w_i = j], j \in \NN$ is defined as follows: 
  Let $m \in \NN$ be the total number of honest participants. 
  Consider the independent Bernoulli random variables $X_i \in \{0, 1\}, i \in [m]$ 
  and a tuple $(\sigma_1, \ldots, \sigma_m) \in [0,1]^m$ 
  so that $\Pr[X_i = 1] = \sigma_i$ 
  and $\sum \sigma_i = 1 - \alpha$. 
  Let $H = H_m = \sum_{i =1}^m X_i$. 
  Then 
  $$
    \Pr[w_i = j] = (1-\alpha)\cdot
      \frac{\Pr[H = j]}{1 - \Pr[H = 0]}
      \qquad \text{for}\quad j = 1,2,3,\ldots
      \,.
  $$
  When $n$ is understood from the context, 
  we write $\mathcal{L}(\alpha)$. 
\end{definition}

For convenience, when $w \sim \mathcal{L}_n(\alpha)$, we write
\begin{align}
  g(n,\epsilon) &= g(W) \qquad \text{where} \quad W \sim \mathcal{L}_n((1-\epsilon)/2) \label{eq:praos-gneps}
\end{align}
\noindent 
Our first goal is to derive tail bounds on $g(n,\epsilon)$. 
We do so by first upper bounding its second moment.




\section{Moments of the grinding power}\label{sec:praos-gp-mgf}
Let $\epsilon \in (0, 1)$ and write $\alpha = (1 - \epsilon)/2$. 
Here, $\epsilon$ is the ``honest bias'' and $\alpha$ is the adversarial stake ratio.
Let $W \sim \mathcal{L}_n(\alpha)$ and 
define 
\begin{align}
    B_{n, \epsilon}(k) 
    &\defeq \Pr[ \#_\A(W_1 \ldots W_n) = k ]  
    = 2^{-n}\binom{n}{k} (1-\epsilon)^k (1 + \epsilon)^{n-k} \nonumber\\
    &=  \binom{n}{k} 
        \left(\frac{1-\epsilon}{2}\right)^n 
        \left(\frac{1 + \epsilon}{1-\epsilon} \right)^{n-k} 
        \,, \label{eq:suffix-prob-binomial}\\
  S(d, z) 
    &\defeq \sum_{i \geq z}^{d-z}{ \binom{d-z}{i} } \label{eq:S_d_z}
    \quad\text{and}\quad \\
  S(d) &\defeq \sum_{z = 0}^{d/2} S(d,z) \label{eq:S_d}
  \,.
\end{align}
Here, $S(d,z)$ is the number of characteristic strings 
of length $d$ where each string contains $z$ honest indices. 
Similarly, $S(d)$ is the number of 



Recall that for any characteristic string $w = w_1 w_2 \ldots$, 
we have $w_0 = 1$ by convention. 
Suppose that $w$ corresponds to a blockchain execution that 
satisfies $\kSlotCP$ and $\sECQ$ properties.
Let $\lambda$ be a positive real, $\lambda \geq 1$. 
Recalling~\eqref{eq:S_y} and~\eqref{eq:g_praos}, 
we can express the $\lambda$th moment of the grinding power as
\begin{align}
    \Exp\, g(W)^\lambda 
    &= \sum_{t = n-s+1}^n \Pr[W_t \neq \A] \cdot \Exp\, (W_t \cdot S(W_{t+1}\ldots W_n))^\lambda \nonumber \\
    &= \sum_{t = n-s+1}^n\,
    \sum_{k \geq 1} 
      \Pr[W_{t} = k] \Pr[\text{$W_{t+1}\ldots W_n$ is $\Aheavy$}]\cdot (k S(n - t) )^\lambda \nonumber\,.
\end{align}
Let
\begin{equation}
  A(\epsilon, \lambda) \defeq \sum_{k\geq 1} \Pr[W_1 = k] \cdot k^\lambda
  \,.
  \label{eq:A}
\end{equation}
Then
\begin{align}
    \Exp\, g(W)^\lambda 
    &= A(\epsilon, \lambda) 
      \sum_{t = n-s+1}^n 
      \Pr[\text{$W_{t+1}\ldots W_n$ is $\Aheavy$}]\cdot S(n-t)^\lambda \nonumber \\
    &=  %\Pr[\text{$W_1$ is honest}]\,
        A(\epsilon, \lambda)
        \cdot 
        \sum_{d=1}^s \sum_{z = 0}^{ d/2 } B_{d, \epsilon}(d - z) S(d,z)^\lambda \label{eq:grinding-power-moment-praos}
\end{align}
where 
and, by convention, 
the inner sum in~\eqref{eq:grinding-power-moment-praos} 
runs for $z = 0, 1, \ldots, \lfloor d/2 \rfloor$.




The first equality in the derivation of~\eqref{eq:grinding-power-moment-praos} follows from 
% the subadditivity of the convex function 
% $x \mapsto x^\lambda$ for $\lambda \geq 1, x \geq 0$,  
~\eqref{eq:g_praos}. 
The second equality follows 
since only $\Aheavy$ suffixes of $w$ contribute to $g(w)$ 
and that the symbols in $W$ are independent. 
The third equality follows from rearranging the sums. 
The last equality follows from~\eqref{eq:suffix-prob-binomial} 
and~\eqref{eq:S_d_z}. 
We remark that in a real execution of Praos, 
the $s$ in~\eqref{eq:grinding-power-moment-praos} 
will be replaced by 
the number of non-empty slots in the last $s$ slots. 


Let $s \in \RR_+$ and $\epsilon \in (0,1)$. 
Define 
\begin{align}
  \phi(\epsilon) &\triangleq \frac{3}{2} \left( (1-\epsilon^2) (1-\epsilon) \right)^{1/3}\label{eq:phi_eps} \\
  V_s(\epsilon) &= \begin{cases}
      \left( (5-3 \epsilon)/2 \right)^s & \text{if}\quad 0 < \epsilon \leq 1/3\,, \\
      \left( 2^{2/3} \phi(\epsilon) \right)^s & \text{if}\quad 1/3 < \epsilon \leq 3/5\,, \\
      \left( (5/3) \phi(\epsilon) \right)^s & \text{otherwise}\,. 
    \end{cases} 
  \,. \label{eq:V-eps-praos}
\end{align}
\noindent
The claims below establish upper bounds to the 
sum in the right-hand side of \eqref{eq:grinding-power-moment-praos}.

\begin{claim}\label{claim:multiple-honest-blocks}
  For $\epsilon \in (0, 1)$, 
  $
    A(\epsilon, 2) 
    % \leq 
    % \frac{(1 + \epsilon)^2 (5 + \epsilon)}{16 \left( 1 - e^{(1 + \epsilon)/2} \right)}
    % \leq 2^{- 0.3 + 1.85 \epsilon}
    % \leq 2^{- 1.3 + 0.41 \epsilon}
    % \leq 1
    \leq 0.8 (1 + 2 \epsilon)
    \,.
  $
\end{claim}
\noindent
In particular, $A(\epsilon, 2) \leq 2.4$. Next, recall $\phi(\epsilon)$ from  \eqref{eq:phi_eps}.

\begin{claim}\label{claim:t1star-variance-exact}
  Let $\epsilon \in (0,1)$ and 
  let $d,z$ be non-negative integers where $d \geq 2$ and $z \leq d/3$. 
  \begin{align*}
    B_{d, \epsilon}(d-z) S(d,z)^2
    &\leq \begin{dcases} 
    \left( (5-3 \epsilon)/2 \right)^d \,,
        &\quad \text{if}\quad
        0 < \epsilon < 1/3 \,, \\
    \left( 2^{2/3} \phi(\epsilon) \right)^d \,,
    %\frac{6}{\sqrt{5 d}}
        &\quad \text{if}\quad
        1/3 \leq \epsilon < 1 \, ,
    \end{dcases}
  \end{align*}
  where $\phi$ is defined in~\eqref{eq:phi_eps}.
\end{claim}

\begin{claim}\label{claim:t2star-variance-exact}
  Let $\epsilon \in (0,1)$ and 
  let $d,z$ be non-negative integers where $d/3 \leq z \leq d/2$. 
  \begin{align*}
    B_{d, \epsilon}(d-z) S(d,z)^2
    &\leq \begin{cases} 
    \left( 2^{2/3} \phi(\epsilon) \right)^d \,,
        &\quad\text{if}\quad 0 < \epsilon \leq 0.6\,, \\
    \left( (5/3) \phi(\epsilon)  \right)^d \,,
        &\quad\text{if}\quad 0.6 < \epsilon < 0.809\,, \\
    1 \,,
        &\quad\text{if}\quad 0.81 \leq \epsilon < 1
        \,.
    \end{cases}
  \end{align*}
\end{claim}
% We defer the proofs of these claims in the next subsection .



The proofs of these claims are presented in next three sections.





\section{Proof of Claim~\ref{claim:multiple-honest-blocks}}\label{sec:praos-claim-multiple-honest-blocks}
\input{grinding-praos/multiple-honest-blocks}


\section{Proof of Claim~\ref{claim:t1star-variance-exact}}\label{sec:praos-claim-t1star-variance-exact}
\input{grinding-praos/second-moment-small-z}


\section{Proof of Claim~\ref{claim:t2star-variance-exact}}\label{sec:praos-claim-t2star-variance-exact}
\input{grinding-praos/second-moment-large-z}












\section{A tail bound for GP from its second moment}
Our goal is to develop tight tail bounds on $g(W)$; 
we do so via tight upper bounds on $\Exp g(W)^2$ 
which, when used in Markov's inequality, 
would give us a tail bound on $g(W)$. 
We remark that the second moment of $g(W)$ grows 
much faster than its first moment. In fact, 
Chebyshev's inequality on $g(W)$ 
fares only marginally better 
than what we get via Markov's inequality on $g(W)^2$. 
This why we relegate the analysis of the first moment 
(which includes both an upper and a lower bound)
in \Section~\ref{sec:praos-mean}.

The three claims above give the following upper bound on $\Exp g(W)^2$.


\begin{lemma}[Second moment of $g$]\label{lemma:grinding-praos-second-moment}
  Let $\epsilon, \EpsP \in (0, 1)$ and $n, k, s \in \NN, s \geq k$. 
  Let $W$ be a characteristic string of length $n$. 
  Let $E$ denote the event that 
  the blockchain protocol $\Blockchain$ 
  satisfies $\kSlotCP$ and $\sECQ$ property throughout 
  the $n$ slots represented by $W$   
  If $W  \sim \mathcal{L}_n((1 - \epsilon)/2)$ then
  \begin{equation}\label{eq:grinding-praos-second-moment}
    \Exp[ g(W)^2 \mid E] 
    \leq 
      0.4 s^2 (1 + 2\epsilon) V_s(\epsilon)
  \end{equation}
  where $V_r(\epsilon)$ is from \eqref{eq:V-eps-praos}. 
  In particular, 
  $$
    \Exp [g(W)^2 \mid E] \leq 1
    \qquad \text{if} \qquad \epsilon \geq 0.809\,.
  $$
\end{lemma}
\noindent
\begin{proof}
  Conditioned on the event $E$, 
  every viable blockchain at the end of slot $n$ 
  must contain at least one honestly-generated block from the last $s$ 
  % non-empty 
  slots.
  Thus, 
  in ~\eqref{eq:grinding-power-moment-praos}, 
  it suffices to consider the suffixes of $W$ of length at most $s$. 
  The factor $s^2/2$ is an upper bound on 
  the number of terms in the double sum in~\eqref{eq:grinding-power-moment-praos}. 
  Note that the bounds in 
  Claims~\ref{claim:t1star-variance-exact} 
  and~\ref{claim:t2star-variance-exact} are monotone increasing in $d$. 
  Hence we use the upper bounds on $B_{s, \epsilon}(s-z) S(s,z)^2$ for 
  different ranges of $z$ and $\epsilon$. 
  Furthermore, by Claim~\ref{claim:multiple-honest-blocks}, 
  % $s^2/2 \cdot A(\epsilon,2) \leq s^2 2^{-1.3 + 1.85 \epsilon}$.
  $A(\epsilon, 2)$ is at most $0.8 + 1.6 \epsilon$. 
  The lemma follows by observing that $s^2/2 \cdot (0.8 + 1.6 \epsilon) = 0.4 s^2 (1 + 2 \epsilon)$.

  For $\epsilon \geq 0.809$, 
  the quantity $V_r(\epsilon) \in (0,1)$ decreases exponentially in $s$ 
  but $s^2/2 \cdot (0.8 + 1.6 \epsilon)$ increases only quadratically; 
  hence the moment is at most one.

  % {\color{blue}Explain the case when the moment is below one.}
\end{proof}

In Figure~\ref{fig:praos-gp-moments}, 
we have plotted various moment bounds on $g(W)$.




\begin{lemma}[Tail bound on $g$ for $W \sim \DistL$]\label{lemma:praos-tail-gamma}
  Let $\epsilon, \EpsP \in (0, 1)$ and $n, k, s \in \NN$. 
  Let $W \sim \DistL_n((1-\epsilon)/2$.
  Consider an execution of a $(\EpsP, k, s)$-secure blockchain protocol within
  the $n$ slots represented by $W$. 
  Let 
  $$
    \text{ $m_s(W)$ be an upper bound on $\Exp[ g(W)^2 \mid E]$}\,.
  $$
  Let 
  \begin{equation}\label{eq:praos-gamma-general-second-moment}
    \gamma_s \geq (m_s(W)/\EpsP)^{1/2}
    \,.
  \end{equation}
  Then 
  $
      \Pr\left[g(W) \geq \gamma_s \right] \leq 2 \EpsP
      % \,.
  $.
\end{lemma}
% The subscript $s$ above indicates that 
% each of the last $s$ slots are non-empty. 
% Recall that the $s$ in~\eqref{eq:grinding-power-moment-praos} 
% is actually the number of non-empty slots in the last $s$ slots. 
% Later on, we will study distribution where this number is different from $s$, 
% i.e., there can be empty slots.
\begin{proof}
  Let us write $\gamma = \gamma_s$.
  Since $g(W)$ is non-negative, observe that 
  $\Pr[g(W) = t] = \Pr[g(W) = t^2]$ for any non-negative $t$. 
  Furthermore, 
  \begin{align*}
    \Pr[g(W) \geq \gamma]
    &= \Pr[g(W) \geq \gamma \mid \overline{E}] \cdot \Pr[\overline{E}] 
      + \Pr[g(W)^2 \geq \gamma^2 \mid E] \cdot \Pr[E]\\
    &\leq 1 \cdot \Pr[\overline{E}] + \Pr[g(W) \geq \gamma \mid E] \cdot 1 \\
    &\leq \EpsP + \Pr[g(W)^2 \geq \gamma^2 \mid E] \\
    &\leq \EpsP + \Exp g(W)^2/\gamma^2 \qquad \text{(by Markov's inequality)} \\
    &\leq \EpsP + m_s(W)/\gamma^2 
  \end{align*}
  by assumption. Since we can control $\gamma$,
  we can make it large enough so that the above quantity is at most $2 \EpsP$. 
  Equivalently, we would want 
  $m(W)/\gamma^2$ to be at most $\EpsP$; 
  this yields~\eqref{eq:praos-gamma-general-second-moment}. 
\end{proof}


\section{Grinding power and beacon quality}
In this section, 
we use the moment bounds from above to derive tail bounds 
on the event that the grinding power is too large. 
We handle the single epoch case first before handling the iterated beacon.

% \Paragraph{Single epoch beacon under $\mathcal{L}$.}~

\begin{theorem}[Praos beacon, single epoch, distribution $\mathcal{L}$]\label{thm:minentropy-loss-praos-single-epoch}  
  Let $\epsilon \in (0,1)$. 
  Suppose Praos 
  remains $(\EpsP, k, s)$-secure 
  inside any epoch 
  whose characteristic string $W$ has the distribution $\mathcal{L}((1-\epsilon)/2)$. 
  Let $\rho$ be the min-entropy loss in 
  the beacon output, $\eta$, after an epoch. 
  Recall $\phi(\epsilon)$ from~\eqref{eq:phi_eps} 
  and $V(\epsilon)$ from~\eqref{eq:V-eps-praos}.
  Let 
  \begin{align}\label{eq:gamma-s-praos}
    \gamma_s = \left( 0.4 (1+2\epsilon) \right)^{1/2} s \cdot V_s(\epsilon)^{1/2} \EpsP^{-1/2}
    \,.
  \end{align}
  Then $$
    \Pr_{W}[g(W) > \gamma_s] \leq 2 \EpsP
    \,.
  $$ 
  % and, consequently, 
  % $$
  %   \Pr_{W}[\rho > 0.5 \log_2 \gamma_s ] \leq 2 \EpsP\,.
  % $$
\end{theorem}
\begin{remark*}
Note that the subscript $s$ in $\gamma_s$ 
arises because the grinding window -- i.e., the last $s$ slots 
in an epoch that contribute in computing the beacon output --  does not contain 
any empty slots. 
% Later, we will use this observation to transfer these results 
% to a distribution which produces empty slots.

For $\epsilon > 0.809$, 
$g(W) = O(s)$ and $\rho = O(\log_2 s)$, 
except with probability $2 \EpsP$.
If $\epsilon < 0.809$, 
$\rho = \Omega(s)$ 
except with probability $2 \EpsP$.  
\end{remark*}

\iftoggle{drawfigs}{
  \input{grinding-praos/fig-praos-single-epoch}
}

% \section{Proof of Theorem~\ref{thm:minentropy-loss-praos-single-epoch}}
\begin{proof}  
  Let $\alpha = (1-\epsilon)/2$ be the adversarial stake.
  Suppose that $\Blockchain$ is $(\EpsP, k, s)$-secure in an epoch 
  where first $n$ slots, 
  which correspond to a characteristic string $W \sim \mathcal{L}_n(\alpha)$, 
  contribute to the beacon output.
  Using Lemma~\ref{lemma:grinding-praos-second-moment} and~\ref{lemma:praos-tail-gamma}, 
  we can see that except with probability $2\EpsP$, $g(W)$ is at most $\gamma_s \defeq \sqrt{m/\EpsP}$ 
  where $m$ is the right-hand-side of~\eqref{eq:grinding-praos-second-moment}.
\end{proof}

% \hfill\qed

% \Paragraph{Iterated beacon under $\mathcal{L}$.}~

\begin{theorem}[Praos beacon]\label{thm:minentropy-loss-praos-multi-epochs}  
  Let $\epsilon \in (0, 1)$ and $L,\kappa \in \NN$. 
  Recall $\phi(\epsilon)$ from~\eqref{eq:phi_eps}.
  Suppose Praos 
  remains $(\EpsP, k, s)$-secure 
  inside any epoch 
  with a characteristic string $W \sim \mathcal{L}((1-\epsilon)/2)$. 
  Let $\gamma_s$ be from ~\eqref{eq:gamma-s-praos} and 
  $\rho = \log_2(\gamma_s)$. 
  % \begin{align}
  %   \rho &= \begin{cases}
  %     % Ignoring the additive factor \log_2(0.4 (1+2\epsilon) )/2
  %     s/2 \cdot \log_2\left( (5-3 \epsilon)/2 \right) + \log_2(s)  & \text{if}\quad 0 < \epsilon \leq 1/3\,, \\
  %     s/2 \cdot \log_2\left( 2^{2/3} \phi(\epsilon) \right) + \log_2(s) & \text{if}\quad 1/3 < \epsilon \leq 3/5\,, \\
  %     s/2 \cdot \log_2\left( (5/3) \phi(\epsilon) \right) + \log_2(s) + 0.14 & \text{otherwise}\,. 
  %   \end{cases}
  %   \label{eq:rho-praos-multiepoch}
  % \end{align}
  Let $\eta \in \{0,1\}^\kappa$ be the output of the beacon after $L$ epochs.
  % and $L \in \NN$ so that $L \sqrt{m \EpsP} \leq 1$. 
  Then $g(W) \leq \gamma_s = 2^\rho$ except with probability at most $3 L s \EpsP^{1/2} V(\epsilon)^{1/2}$.
  Equivalently,
  $$
    \Pr_{W \sim \mathcal{L}((1-\epsilon)/2)}[H_\infty(\eta) \geq \kappa - \rho] 
      \leq 1 - 3 L s \EpsP^{1/2} V_s(\epsilon)^{1/2} \,.
  $$
  In particular, for $\epsilon > 0.809$, 
  $\rho = \Poly(\log_2 s)$ and $g(W) = O(s)$ 
  except with probability at most $3 L s \EpsP^{1/2}$.
\end{theorem}
% \noindent
% The proof of Theorem~\ref{thm:minentropy-loss-praos-multi-epochs} 
% is presented in Section~\ref{sec:proof-praos-theorem}. 

\begin{remark*}
  When $\epsilon < 0.809$, 
  the $O(s)$ term in the min-entropy loss $\rho$ 
  is inevitable since, at this region, 
  $g(W) = e^{\Omega(s)}$.
  The factor $1/2$ in the leading term in $\rho$ 
  is the result of using the second-moment method 
  to derive the tail bound.
\end{remark*}

\begin{proof}
  % Let $W \sim \mathcal{L}_n(\alpha)$. 
  Let $E$ be the event that 
  $\Blockchain$ is not $(\EpsP, k, s)$-secure during 
  the first $n$ slots in an epoch. 
  Let $m$ be an upper bound on the second moment of $g$, 
  conditioned on $\overline{E}$. 
  Let $\gamma_s \geq (m/\EpsP)^{1/2}$. 
  Let $E_g$ be the event that $g(W)$ is more than $\gamma$.
  By Lemma~\ref{lemma:grinding-praos-second-moment}, 
  $\Pr[g(W) \geq \gamma_s] \leq 2 \EpsP$. 
  Note that the min-entropy loss in the beacon is at most 
  \begin{equation}\label{eq:log-gamma}
   \log_2(\gamma_s) 
   = 1/2 \cdot [\log_2(m) + \log_2(1/\EpsP)]
   = \log_2(\sqrt{m}) + \log_2(1/\sqrt{\EpsP})
   \,. 
  \end{equation}


  Condition on the event that neither $E_p$ nor $E_g$ 
  occurs during the first $L$ epochs. 
  This means, in any of the $L$ epochs, 
  the adversary can inflate the failure probability 
  by at most a factor of $\gamma_s$.
  The total bad probability after $L$ epochs is
  $$
    p
    \leq L (2 \EpsP + \gamma_s \EpsP)
    = L (2 \EpsP + m^{1/2} \sqrt{\EpsP})
    \,.
  $$

  Since $\epsilon > 0.809$, we refer to \eqref{eq:V-eps-praos} 
  and the statement of the theorem immediately follows.
  % \hfill\qed
\end{proof}

% \iftoggle{drawfigs}{
%   \input{grinding-praos/fig-praos-multi-epoch}
% }










% \section{Lifting the analysis to handle empty slots}\label{sec:praos-empty-slots}


%   \begin{definition}[$\mathcal{M}_n(\alpha, f)$]\label{def:dist-M-alpha-f-praos}
%     Let $\alpha \in (0,1/2), f \in (0,1)$, and $n \in \NN$. 
%     $\DistM_n(\alpha, f)$ is a distribution on characteristic strings 
%     $w = w_1 \ldots w_n$ so that 
%     the symbols $w_i$s are independent and identically distributed, as follows: 
%     with probability $1-f$, $w_i = \perp$ 
%     and, with probability $f$, 
%     $w_i$ is distributed as $\DistL_1(\alpha)$ (Definition~\ref{def:dist-L-alpha-praos}).
%     When $n$ is understood from the context, 
%     we write $\DistM(\alpha, f)$. 
%   \end{definition}
%   \noindent
%   It follows that under $\DistM(\alpha, f)$ and for all $i$,
%     $\Pr[w_i = \A] = f \alpha$ and $\Pr[w_i = \perp] = 1-f$, and 
%     $$
%       \Pr[w_i = j] = f (1-\alpha)\Pr[H = j]/Pr[H \geq 0]
%         \qquad \text{for}\quad j = 1,2,3,\ldots
%     $$
%   If a symbol $w_i \sim \DistM_1(\alpha,f)$ then it means as follows: 

%   Let $\alpha \in (0,1/2)$ and $f \in (0,1)$. 
%   Focus on the execution of an $(\EpsP, k, s)$-secure blockchain execution over a single epoch.
%   Let $W$ be the corresponding characteristic string with distribution $\DistM_n(\alpha, f)$.
%   Condition on the event $T_{s,r}$ that at least $r$ out of the last $s$ slots in $W$ are non-empty. 
%   It is easy to see that $r \sim \Binomial(s, f)$.
%   Consider the conditional grinding power for a single epoch, $g_r = g(W | T_{s,r})$.
%   % Theorem~\ref{thm:minentropy-loss-praos-single-epoch} and the remark thereafter 
%   % imply that $g_r$ satisfies  
%   Define, in accordance with Lemma\ref{lemma:praos-tail-gamma}, 
%   \begin{align*}
%     m_r    &= 0.4 (1 + 2\epsilon) r^2 V_r(\epsilon)\,, \\
%     \gamma_r  &= \sqrt{m_r/\EpsP}\,.\qquad\text{and}\\
%     P_r       &\defeq \Pr[ g_r \geq \gamma_r \mid T_{s,r}]\,.
%   \end{align*}

%   Now, let us focus on the grinding power in a single epoch.
  
%   \newcommand{\EpsR}{\varepsilon_R}

%   Let $\delta \in \RR_+$ whose value will be chosen later.
%   Let $R = (1+\delta) Sf$
%   Let us write $g = g(W)$. 
%   Total failure probability for this epoch is $\EpsR + P_R$, where 
%   \begin{itemize}
%     \item $\EpsR \defeq  \Pr[r \geq R] \leq e^{-\delta^2 Sf/3}$ by a standard Chernoff bound.
%     \item $P_R\defeq \Pr[ g_R \geq \gamma_R \mid T_{s,R}]$, the probability that 
%     either $g_R > \gamma_R$ 
%     or the blockchains was not $(\EpsP, k, s)$-secure in this epoch.
%   \end{itemize}
%   By Lemma\ref{lemma:praos-tail-gamma}, $P_R \leq 2 \EpsP$.


%   % Repeating our footsteps in Lemma~\ref{lemma:praos-tail-gamma}, we write
%   % \begin{align*}
%   %   \Pr[g(W) > \gamma_R] 
%   %   % &= \sum_{i \geq R} \Pr[T_{s,i}] \cdot \Pr[g(W) > \gamma_s | T_{s,i}] 
%   %   %   + \sum_{i < R} \Pr[T_{s,i}] \cdot \Pr[g(W) > \gamma_i | T_{s,i}] \\
%   %   &\leq \Pr[r \geq R] \cdot \Pr[g_s > \gamma_s | T_{s,s}] + \Pr[r < R] \cdot \Pr[g_r > \gamma_R | T_{s,R}] \\
%   %   &\leq \Pr[r \geq R] \cdot P_s + \Pr[r < R] \cdot P_R
%   %   &= 2 \EpsP
%   % \end{align*}
%   % since both $P_s$ and $P_R$ are at most $2 \EpsP$.

%   Now let us consider the iterated beacon over $L$ epochs. 
%   As we showed in the proof of Theorem~\ref{thm:minentropy-loss-praos-single-epoch}, 
%   the failure probability will be at most $L \cdot (2 \EpsP + e^{-\delta^2 Sf/3} + \gamma_R \EpsP)$. 
%   As we can control $R$ by selecting an appropriate $\delta$, 
%   we should be able to control the preceding quantity as well.

%   Now, $\gamma_R \EpsP = \sqrt{m_R \EpsP} \leq 1.1 R V_R(\epsilon)^{1/2} \EpsP^{1/2}$

 



