  It was a dreary, cold, and gray December day. When I picked up \emph{that} book at UConn's library, 
  I didn't know that in about ten years in the future, 
  I would be writing this acknowledgment. 
  Thank you, \emph{Men of Mathematics.} And thank \emph{you}, 
  Euler, Gauss, Galois, and Riemann. If you weren't there, 
  I wouldn't be here.

  \AckBreak
  Thank you, Lara (Chiaverini), Joy (Billion), Rebecca (Randazzo), 
  Debra (Mielczarek), and Howard (Ellis)! 
  I didn't realize that we've been here for a decade. 
  I loved to bug you guys at the department office. 
  I'm immensely grateful to the C.S. department 
  for letting me print thousands of pages. 
  Without these, I would never have been able to graduate.

  Thank you, Sarah (Peck), Luke (Johnson), Jordan (Force), Sanjiv (Dinakar), 
  Eli (Sherafat), Badar (Almarri), Gang (Wang), and Saurav (Dhar). 
  You guys made the lab a truly remarkable place and 
  I'll always cherish your company.

  Thank you, Alina (Tuminska)! 
  You used to come late to our labs 
  and set things in order. 
  You didn't speak much 
  but you smiled bright, and 
  the warmth of your heart 
  shone through. 
  It always felt great talking to you. 
  
  \AckBreak
  Thank you, Aggelos (Kiayias) and Peter (Ga\v{z}i)! 
  Although I spent only a limited time with you, 
  I've spent a lot of time with your work 
  and it's been an honor. 
  Also, I'm grateful to IOHK for generously supporting my research 
  over the years.

  Thank you, Cris (Moore)! You've been an inspiration to me. 
  Although we've never spoken, 
  you loomed large in my mind through the image I got from Professor Russel,
  your tour de force analyses, 
  and the magnum opus that is \emph{The Nature of Computation.}

  Thank you, Ion (Mandoiu), Mukul (Bansal), and Walter (Krawec)! 
  You have shown me unparalleled kindness and appreciation over the years.

  Thank you, Raj (Sanguthevar Rajasekaran). 
  It was your ``Randomized Algorithms'' course that 
  opened my eyes to the beauty and simplicity 
  in randomized algorithms.

  Thank you, Don (Sheehy)! I fondly remember 
  the many hours we've spent discussing 
  computer science. 
  Your love for the game shines through, do you know that? 

  Thank you, Ben (Fuller)! 
  When you first came, 
  you used to have this weekly lunch with me 
  despite all your pressing commitments. 
  There, while talking to you, 
  I first appreciated the value in speaking precisely. 
  Over the years, 
  you've given me concise advice---about my writings, my work, my approach to CS, etc.---that 
  have helped me correct course and grow. 
  I am immensely fortunate to have you as my mentor.
  You are the most awesome classroom teacher I've seen.

  \AckBreak
  Thank you, Yao (Ren) and Vijay (Raghavan)! 
  You have taken a big chance on me in taking me in at MathWorks. 
  Yao, I will be forever indebted to you for 
  giving me time and space 
  for preparing this dissertation.

  \AckBreak
  Thank you, my friends: Ahsan (Karim), Ashik (Rahman), 
  Redwan (ul Haq Choyon), Saikat (Islam), Shafiul (Islam), 
  Kaptan (Istiaque Hasan), Kajal (Jahid), 
  Farzan (Ahmed), and Mahadi (Rahman)! 
  You have made me \emph{me} over the years. For good or for bad.

  Thank you, Shakil vai, Fahim, Lazin, Nafis, Abhijit, 
  Bashar, Tasnuva, Anik, and Nisha! 
  It's been a pleasure to have you in my life. 
  Saiful vai, Fahim, and Lazin, 
  I can't really do justice to you here, but here's to you!

  Thank you, Mehdi (Anwar) Sir and (Sarah Tasneem) Lia Ma'am! 
  You have been there when I needed guidance and advice. 
  Those gatherings in your home were 
  a glue to our community. 
  How I loved your delicious food and witty exchanges :)
  
  Thank you, Maifi (Hasan Khan) Sir and Liza apu! 
  Your warmth was off the charts. 
  Liza apu, you are my most favorite apu. 
  But it was you---Maifi Sir---who told me to shore up courage and ask 
  Professor Russell whether he would take me as his student. 
  It was the last day of the semester and 
  it was clear that things were not working out between me and my then Ph.D. adviser. 
  I didn't know what to do after five years in the graduate school. 
  I never thought of approaching Professor Russell---I never thought he would take me as his student. 
  But you said, why not just ask? 
  I told you to wait ten minutes, rushed to his room, 
  asked him, and now you are reading this line in my dissertation :)

  Thank you, my teachers in my formative years: 
  Swapan Dhar Sir, Deepak Sir, Selina Madam, Asaduzzaman Sir, Mushfiq Sir, Hossain Sir, and Vutto Sir! 

  Thank you, Hajan Uncle! You didn't flinch when you gave my dad the hefty money 
  needed for my I-20 at UConn. He didn't even have to ask.

  Thank you, Panna Uncle, Beauty Bouma, Kabir Uncle, Prova Chachi, Jewel Fufi, and Kowel Fufi! 
  It is your love that doesn't let me age.

  Thank you, Bubu. You have cradled me when I was young. 
  You have loved me unconditionally, for ever.

  Thank you, Tayeeb. I was able to do this Ph.D. because you were there back with my mum and dad.


  \AckBreak
  It would have been very difficult to finish the graduate school 
  without occasional, timely, and unflinching financial support 
  (i.e., personal loans) from you, my friends and family. 
  I am not going to name you here, but \emph{thank you!}


  \AckBreak
  And then there's you, Mukti. 
  This dissertation is written with the ink of your tears, 
  your agonies, your sacrifices, your patience, your blood. 
  But it is also written with the joys we've shared, 
  the places we've been, 
  the peaks we've scaled, 
  the streams we've waded, 
  the towering mountains we've gazed at, 
  the grasslands and salt flats we've lied on,
  the two bison that walked past us, 
  the bear cubs that we missed to photograph, 
  the stars that shone upon us from the desert sky, 
  the El Capitan cliff that you brought by my side, 
  and the night we got lost in the Adirondack woods.

I've been so happy to be with you 
  that I didn't notice that you are brightening my life 
  like a candle does. 
  I would never have been able to finish up this Ph.D. had it not been for you. 
  You've sacrificed your life, your career, and your time for me. 
  You are a girl with a big, big heart. 
  I love you.
  

 \AckBreak
 Thank you, Sadia, Shinjon, and Saba. You've made me so happy just by being who you are. 
 I miss you all so much. 
 I can't do justice to you here, you know that.


 Thank you, \emph{Ma} and \emph{Baba}! 
 It's hard to put in words what I want to tell about you. 
 You are the most compassionate and unselfish parents that one could possibly have. 


 Ma and Baba, you have always appreciated me and 
 taken pride in me.  
 You taught me how to love reading books. 
 Ma, when I was in class two, you got me two books from Dhaka: 
 one was Aesop's Fables and the other was a Children's Encyclopedia. 
 When I was in class three, Baba, you got me another Children's Encyclopedia.
 In class five, you went to Netrokona and got me thirty-three books, 
 mostly science-related. 
 In class five, you sent me off with Ishaq Uncle to the fabled book fair in Dhaka, 
 with \emph{one-thousand taka} to buy any book I like. 
 These books have had a profound impact on me. 


 Ma, you fought with your family for many years to 
 protect your education. 
 You got into the Dhaka University's English language masters program 
 but could finish it. 
 You had to marry, relocate to Mymensingh, 
 and start your family. 
 But you set out to do for your kids what you couldn't do in your life. 
 You prioritized the education for all your kids. 
 All your four kids got to like studying in school 
 and some of them (read: Shinjon) really became a star. 
 Ma, it is for your vision and sacrifice that 
 we, your kids, are here.

 Ma, you taught me English grammar and present-past-future tense 
 long before they were taught in school. 
 It was because of you that I got to like the language 
 and always got high marks in the exams. 
 Not only that, 
 when I came in the U.S., 
 in numerous occasions, 
 people remarked that I speak good English. 
 They don't know about you, Ma, 
 but it was thanks to you.

 Ma, remember, when in class two, 
 in the English exam, I wrote the sentence 
 ``make me a cake;'' you taught me this grammar. 
 But my school teacher disagreed: 
 she said, ``you want to buy a cake, not \emph{become} a cake.'' 
 Well, Ma, you were right all along. 
 You taught your kid the right grammar. 
 How could you not?

 Ma, you always looked for ways to get the best for me. 
 One day, you dropped me off to school and were coming back home; 
 it was a hot day. 
 On your way walking home, you had a close call with a traffic accident. 
 Do you remember why you were walking home? 
 Instead of taking a rickshaw (which would have cost two \emph{takas}), 
 you chose to buy two guavas for me because---everyone knows---guavas are good for children.


 Ma, I can hardly imagine how hard it was emotionally for you 
 to put your son in the Cadet College for six years. 
 But you put up a tough face and did what was good for me. 
 Those were the best days of my life. 
 I learned that anything is possible. 


 When I was in class nine, 
 the S.S.C. board exam was in two years. 
 You were speaking with one of my teachers 
 and you said, ``I want him to become one of those top-twenty 
 students, those who \emph{stand} in the exam.'' 
 I was surprised. (The audacity of dreams, come to think of it.) 
 But this is classic you, Ma, 
 dreaming and expecting big things for your kids, 
 things that we never thought was possible.

 \vspace{1em}

 Baba, I was in class six and you were taking me somewhere on your motorcycle. 
 You stopped to speak with someone in front of a shop. 
 I was longingly looking at a hand-held video game console; 
 these Tetris game consoles were the rage those days. 
 You noticed, and asked the man; he said it was two hundred takas. 
 \emph{Two hundred}. Not in my league. Maybe I sighed. 
 You drove back home, got the money, drove to the shop again 
 and got me the console, to my utter disbelief. 
 Two hundred takas was not a small amount of money at that time, and we didn't have the luxury for these indulgences.
 But you didn't flinch. 
 That day, I promised to myself that I'd do anything for you. 
 (I didn't keep this promise very well, Baba.)

 You never lacked imagination. 
 A few days before my S.S.C. exam, I was heading out to buy pens. 
 You tagged along and ended up buying me \emph{one hundred and six} 
 different pens, pencils, and refills. 
 In 1992, when they were laying down submarine Internet cables under the ocean, 
 you got two landlines home because---everyone knows---you'll need one dedicated line 
 when you get hooked to the Internet. 
 You \emph{are} one in a million.

 Another day, we were having lunch at home. 
 You came to the table a little late and, 
 right before you put the food in your mouth, 
 you noticed that my eyes were swelling with tears. 
 The doctor told me not to have beef as I was having an allergy. 
 You stopped then and there, took me on the motorcycle, 
 drove to the \emph{Minar Hotel} behind the \emph{Boro Masjid} 
 and got me some mutton. 
 This is a silly story, Baba, 
 but my eyes still swell when I remember the kindness. 
 You couldn't eat your food when I could not.

 I hope I've made both of you proud. 

\AckBreak
Thank you, my Ph.D. committee members, Dr. Benjamin Fuller and Dr. Walter Krawec! 
You have helped me navigate a tricky time in my career. 
You have trusted me, gave me feedback, and helped me grow. 
I am immensely grateful to you.

 \vfill
 \begin{center}(This space is left blank, intentionally.)\end{center}
 \vfill
 \newpage

  \AckBreak
  The Sanskrit word \emph{Dvija} refers to a Brahmin priest who is  
  ``born twice'' after he earns his place in the clergy. 
  But I intend to take the word literally. 
  Professor Russell, I've had a new life since I've become your student. 

  You trusted me, let me make mistakes, never flinched, never doubted, 
  never frowned. You made me feel that I'm walking the same path that Riemann had walked before, 
  but it's taking a bit longer because, well, there's no shame if you can't be Riemann. 
  You gave me time, oh how sorely did I need that. 
  
  Once we were discussing and the term ``homomorphism'' came up. 
  (Dear reader, it is a basic but important term in algebra.)
  In my mind, I was mixing it up with ``homeomorphism'' 
  and, when I asked you what it was, you went on into an hour-long 
  introduction to Representation Theory. 
  You could have told me ``Oh, don't you know that?'' but you didn't. 
  If only I could be as patient, as humble, and as deep as you are.

  I am most fortunate to be your student. 
  I've seen the dynamic between other graduate students and their advisers. 
  In terms of being awesome, you are in a league of your own.

  You've taken care of me: financially, spiritually, and academically. 
  Ever since I've known you, I wanted to be like you. I still do. I always will. 
  You've given a richness to my life you'll never know.
  I hope I'll grow to be worth the unconditional love, patience, and respect you've given me. One day. 
  I hope to be like you.
  % Speaking with you in your room was an amazing experience. 

  \emph{Thank you,} Professor Russell, for giving me this amazing ride 
  both in life and in computer science.

 \vspace{1in}
 \begin{flushright}
  Saad Quader\\
  12/04/2020   
 \end{flushright}
