%%%---- Do not adjust ----%%%
\documentclass[11pt,oneside]{book}
% \documentclass[11pt,oneside,draft]{book}
\input{preamble.tex}
%%%-----------------------%%%

%Add your data to the following commands.
%%%%%%%%%%%%%%%%%%%%%
\newcommand{\mythesistitle}{Security of Proof-of-Stake Blockchains}
\newcommand{\myname}{Saad Altaful Quader}
\newcommand{\myyear}{\the\year}
\newcommand{\degreeone}{B.S., Bangladesh University of Engineering \& Technology, 2007}
\newcommand{\degreeoneshort}{B.S.}
\newcommand{\degreetwo}{M.S., University of Connecticut, 2013}
\newcommand{\degreetwoshort}{M.S.}
\newcommand{\majoradvisor}{Alexander Russell}
\newcommand{\associateone}{Benjamin Fuller}
\newcommand{\associatetwo}{Walter Krawec}
%%%%%%%%%%%%%%%%%%%%%

%%%---- Do NOT adjust ----%%%
\begin{document}
\input{frontmatter.tex}
\singlespacing

\setcounter{tocdepth}{1}
\tableofcontents

\listoffigures
\begingroup
\let\clearpage\relax% Disable newpage before list of tables
\listoftables
\endgroup


\thispagestyle{plain}
\mainmatter
\doublespacing
% \singlespacing
%%%-----------------------%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%---- Input content ----%%%


\chapter{Introduction}\label{sec:intro-main}
\Epigraph{
  Sorry! I don't want any adventures, thank you. Not Today. Good morning! 
  But please come to tea---any time you like! 
  Why not tomorrow? Good bye!
  }{Bilbo Baggins \\ The Hobbit}
\input{intro-new}

\chapter{Nakamoto-style PoS Blockchains: A Primer}\label{sec:pos-primer}
\Epigraph{
  Ho! Tom Bombadil, Tom Bombadillo!
  By water, wood and hill, by the reed and willow,
  By fire, sun and moon, harken now and hear us!
  Come, Tom Bombadil, for our need is near us!
  }{Frodo Baggins \\ The Lord of the Rings}
\input{pos-primer}

\renewcommand{\PartPrefix}{multihonest}
\part{The Consistency Problem}\label{part:multihonest}
\input{multihonest}

\renewcommand{\PartPrefix}{praos}
\part{The Grinding Problem}\label{part:praos}
\input{grinding-praos}

\renewcommand{\PartPrefix}{xorgames}
\part{Secure Beacons for Eventual Consensus}\label{part:xorgames}
\input{xorgames}


%... etc.
%%%-----------------------%%%
\cite{}
\singlespacing
\newpage
\addtocontents{toc}{\protect\setChapterprefix{}}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plainnat}  
\bibliography{bib/thesis,bib/forks,bib/grinding,bib/abbrev0,bib/crypto_crossref}

\appendix
\addtocontents{toc}{\protect\setChapterprefix{Appendix }}

\chapter{Stirling's Approximation and Binomial Coefficients}\label{app:binomial-coeff}
\input{grinding-praos/app-binomial-coeff}

% \chapter{Fractional moment bounds for the geometric distribution}\label{app:geometric}
% \input{xorgames/geometric.tex}

% \chapter{Poisson distribution is subgeometric}\label{app:poisson}
% \input{xorgames/poisson.tex}




\end{document}