


\tikzsetexternalprefix{\PartPrefix}


\chapter{The Consistency Problem}\label{sec:intro-multihonest}
\Epigraph{
  Begin at the beginning and go on till you come to the end: then stop.
}{
  Lewis Carroll \\ Alice in Wonderland
}
\input{multihonest/intro}

\chapter{The Settlement Security Model}\label{sec:model-multihonest}
\Epigraph{
  Ezekiel 25:17. 
  The path of the righteous man 
  is beset on all sides  
  by the inequities of the selfish 
  and the tyranny of evil men.  
}{
  Jules Winnfield \\ Pulp Fiction
}
\input{multihonest/model}
% \input{multihonest/definitions}\label{sec:definitions-multihonest}

\chapter{Catalan Slots and the UVP}\label{sec:catalan}\label{sec:definitions-multihonest}
\Epigraph{
  The first rule of Fight Club is: You do not talk about Fight Club. \\
  The second rule of Fight Club is: You do not talk about Fight Club.
}{
  Tyler Durden \\ Fight Club
}
\input{multihonest/definitions}
\input{multihonest/fork}
\input{multihonest/catalan-cp}


\chapter{Proving UVP without Catalan Slots}\label{sec:fork-framework}
\Epigraph{
  ``If by my life or death I can protect you, I will.''   
}{
  Aragorn, Son of Arathorn \\ The Lord of the Rings
}
\input{multihonest/fork-framework}


\chapter{Tail Bounds for Catalan Slots; Proof of the Main Theorem}\label{sec:bounds-main-proofs-multihonest}
\Epigraph{
``You cannot pass,'' he said. 
The orcs stood still and a silence fell. 
``I am a servant of the Secret Fire, wielder of the Flame of Anor. 
You cannot pass. The dark fire will not avail you, flame of Ud\^{u}n. 
Go back to the Shadow. You cannot pass!''  
}{
  Gandalf the Grey \\ The Lord of the Rings
}
\input{multihonest/bounds}

\chapter{A Random Walk on Characteristic Strings}\label{sec:rand-walks}
\Epigraph{
  Begin at the beginning and go on till you come to the end: then stop.
}{Lewis Carroll \\ Alice in Wonderland}
\input{multihonest/randwalk} 


\chapter[Proving the Tail Bound]{Proof of \texorpdfstring{Bound~\ref{bound:unique-honest-catalan}}{the First Tail Bound} }\label{sec:estimates-multihonest}
\Epigraph{
  All that is gold does not glitter, \\
  Not all those who wander are lost; \\
  The old that is strong does not wither, \\
  Deep roots are not reached by the frost.
}{
  Bilbo Baggins \\ The Lord of the Rings
}
\input{multihonest/estimates}


\chapter{An Optimal Attack against Consistency}\label{sec:opt-adversary}
\Epigraph{
  Do not go gentle into that good night,
  Old age should burn and rave at close of day;
  Rage, rage against the dying of the light.  
}{
  Professor Brand \\ Interstellar
}
\input{multihonest/opt-adversary}


\chapter{Proofs of Theorem~\ref{thm:relative-margin} and Theorem~\ref{thm:opt-adversary-canonical}}\label{sec:margin-proof-multihonest}
\Epigraph{
``As far back as I can remember, I always wanted to be a gangster.''
}{
  Henry Hill \\ Goodfellas  
}
\input{multihonest/margin-proof}


\chapter{A Consistent Longest-Chain Tie-Breaking Rule}\label{sec:lcr-tie-multihonest}\label{sec:lcr-model}
\Epigraph{
  ``What we've got here is failure to communicate.  ''
}{
  Captain \\ Cool Hand Luke
}
\input{multihonest/tie-breaking}


\chapter{The Semi-synchronous Setting}\label{sec:async-multihonest}\label{sec:async-model-multihonest}
\Epigraph{
Arise, arise, Riders of Th\'{e}oden! 
Fell deeds awake: fire and slaughter! 
Spear shall be shaken, shield be splintered, 
a sword-day, a red day, ere the sun rises! 
Ride now, ride now! Ride to Gondor!  
}{
  King Th\'{e}oden of Rohan \\ The Lord of the Rings
}
\input{multihonest/async}


\chapter{Common Prefix Property (CP)}\label{sec:cp-multihonest}\label{sec:cp-model-multihonest}
\Epigraph{
  ``Well, I just... Y'all's the onliest family I got. 
        I love the 54th. Ain't even much a matter what happens tomorrow, 'cause we men, ain't we?''  
}{
  Trip \\ Glory
}
\input{multihonest/cp}


\chapter{History-Dependence in Leader Elections}\label{sec:martingale}
\Epigraph{
  ``I see dead people!''  
}{
  Cole Sear \\ The Sixth Sense
}
\input{multihonest/martingale}


\chapter{Explicit Error Estimates}\label{sec:exact-prob-multihonest}
\Epigraph{
  ``My life amounts to no more than one drop in a limitless ocean. 
  Yet what is any ocean, but a multitude of drops?''  
}{
   Luisa Rey \\ Cloud Atlas
}
\input{multihonest/exact-probabilities}

