% \small{
% \begin{enumerate}
%     \item Which problem are we talking about?
%     \item What should a desired solution do?
%     \item What have others done about it?
%     \item What is still missing?
% \end{enumerate}
% }

The heartbeat of a blockchain protocol is the periodic flashes from its \emph{randomness beacon}. 
In every period, the players agree on a random string without resorting to any trust. 
This random string fuels a flurry of activities, 
culminating in the selection of another random string for the next period, ad infinitum. 
% In fact, any distributed protocol that periodically needs random strings must use a randomness beacon. 

It is pivotal that the beacon is \emph{bias-resistant}, 
which means the periodic outputs must be statistically close to the uniform distribution. 
The beacon must be \emph{unpredictable} as well, which means no one can predict the outcomes except with a negligible probability. 
In addition, it has to be \emph{publicly verifiable}, 
which means anyone can use publicly available information to verify each step of the computation. 
Finally, it must provide \emph{liveness}, which means (i.) that the beacon always produces its periodic output 
and (ii.) everyone receives the same output. 

Consider a proof-of-stake (PoS) blockchain protocol [reference] 
where it is practically ``free'' to query the random oracle 
which is often implemented as a verifiable cryptographic hash function (VRF).
A malicious coalition in the beacon sub-protocol can evaluate the VRF multiple times (say, $q$ times) 
before committing to their ``favorite'' VRF outputs. 
Indeed, this increases the probability that the resulting beacon value sways the future events in the adversary's favor. 
This is the \emph{grinding attack} against the protocol and it is easy to see that 
it is in fact an attack against the bias-resistance property of the beacon. 
The quantity $q$ is called the grinding power of the adversary.

The security analysis of the state-of-the-art PoS blockchain protocols [reference] 
\emph{assumes} that the grinding power $q$ is bounded by $\Poly(k)$ 
where $k$ is a security parameter of the blockchain protocol. 
% A decentralized randomness beacon [reference] is typically used in conjunction with an ambient decentralized protocol.
% Naturally, any security guarantee for the ambient protocol hinges on the security of the beacon 
% since an attack against the beacon can be converted, in principle, as an attack against the ambient protocol.
% For example, consider the \emph{grinding attack} on the eventual consensus-based proof-of-stake blockchain protocol [where?].
% Under the hood, this attack is actually performed on the bias-resistance property of the randomness beacon.
% The security proofs of the state-of-the-art PoS protocols [Ouroboros, Snow White], however, do not 
% quantify the ``grinding power'' (i.e., the number of random oracle queries) of a malicious coalition. 
% Instead, these proofs assume that this number is bounded by a polynomial in the security parameter. 
This leaves us with some open questions. For example, 
\emph{how does the grinding power grow as a function of the adversarial stake? 
When is it indeed $\Poly(k)$?}

\paragraph{Our contributions.} 
\begin{itemize}
    \item We design a randomness beacon with a guaranteed min-entropy. 
    Specifically, given an arbitrary failure probability $\EpsP$, 
    we describe a function $\gamma$ which gives an upper bound on the quantity $q$ above, i.e., 
    it captures the grinding power of the the adversary.
    The loss in the min-entropy of our beacon in a single period is at most $\log_2 \gamma$ except with probability $\EpsP$. 
    
    \item As an immediate application, we use this beacon to design a PoS blockchain protocol 
    which has a public leader-schedule (like Ouroboros) and a simple-to-describe VRF-based beacon (like Praos).
    
    \item At last but not the least, we provide, for the first time, a rigorous analysis of the grinding attack 
    against Praos. 
    Our analysis shows that the grinding power in Praos is indeed $\Poly(k)$ if the adversarial stake is at most $10\%$.
\end{itemize}

% Or equivalently, what is the min-entropy of the underlying randomness beacon as a function of the adversarial stake?
% What is the quantitative relationship between the security properties (e.g., the min-entropy) of a beacon 
% and those (e.g., epoch length) of the ambient protocol? 

% Specifically, we show that as long as the ambient protocol guarantees eventual consensus and 

% This brings us to the randomness beacons in general. 






\paragraph{The problem.} 
Can a set of mistrustful parties agree on a random string that is unbiased, unpredictable, 

\subsection{Overview of this work}
\begin{enumerate}
    \item What do we bring to the table? How do we define security and how do we meet it?
    \item How does it complement the landscape? What are the assumptions?
    \item What are some immediate applications?
    \item What are some interesting things under the hood?
\end{enumerate}

\subsection{Background and related work}
\label{sec:related-work}
\input{tex/related-work.tex}

\subsection{Organization of this paper}